Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-18 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
reordered code chunks & removed call with 'ord2'

```{r, define-contrasts-{{hot_chr}}}
contrasts_BC_FG <- local_nonlocal_annot %>%
  ungroup() %>%
  select(symbol, cA:cH, local_tx, lod) %>%
  (function(x) x[ord2, ]) %>%
  mutate(row_num = 1:nrow(local_nonlocal_annot), 
         AB = abs(cA - cB),
         AC = abs(cA - cC),
         AD = abs(cA - cD),
         AE = abs(cA - cE),
         AF = abs(cA - cF),
         AG = abs(cA - cG),
         AH = abs(cA - cH),
         BC = abs(cB - cC),
         BD = abs(cB - cD),
         BE = abs(cB - cE),
         BF = abs(cB - cF),
         BG = abs(cB - cG),
         BH = abs(cB - cH),
         CD = abs(cC - cD),
         CE = abs(cC - cE),
         CF = abs(cC - cF),
         CG = abs(cC - cG),
         CH = abs(cC - cH),
         DE = abs(cD - cE),
         DF = abs(cD - cF),
         DG = abs(cD - cG),
         DH = abs(cD - cH),
         EF = abs(cE - cF),
         EG = abs(cE - cG),
         EH = abs(cE - cH),
         FG = abs(cF - cG),
         FH = abs(cF - cH),
         GH = abs(cG - cH)
  ) %>%
  mutate(BC_A = abs((cB + cC) / 2 - cA),
         BC_D = abs((cB + cC) / 2 - cD),
         BC_E = abs((cB + cC) / 2 - cE),
         BC_F = abs((cB + cC) / 2 - cF),
         BC_G = abs((cB + cC) / 2 - cG),
         BC_H = abs((cB + cC) / 2 - cH),
         BC_FG = abs((cB + cC) - (cF + cG))
         ) %>%
  select(symbol, BC_FG)

@@

>>>>

@@

```{r, define-contrasts-{{hot_chr}}}
contrasts_BC_FG <- local_nonlocal_annot %>%
  ungroup() %>%
  select(symbol, cA:cH, local_tx, lod) %>%
  mutate(row_num = 1:nrow(local_nonlocal_annot), 
         AB = abs(cA - cB),
         AC = abs(cA - cC),
         AD = abs(cA - cD),
         AE = abs(cA - cE),
         AF = abs(cA - cF),
         AG = abs(cA - cG),
         AH = abs(cA - cH),
         BC = abs(cB - cC),
         BD = abs(cB - cD),
         BE = abs(cB - cE),
         BF = abs(cB - cF),
         BG = abs(cB - cG),
         BH = abs(cB - cH),
         CD = abs(cC - cD),
         CE = abs(cC - cE),
         CF = abs(cC - cF),
         CG = abs(cC - cG),
         CH = abs(cC - cH),
         DE = abs(cD - cE),
         DF = abs(cD - cF),
         DG = abs(cD - cG),
         DH = abs(cD - cH),
         EF = abs(cE - cF),
         EG = abs(cE - cG),
         EH = abs(cE - cH),
         FG = abs(cF - cG),
         FH = abs(cF - cH),
         GH = abs(cG - cH)
  ) %>%
  mutate(BC_A = abs((cB + cC) / 2 - cA),
         BC_D = abs((cB + cC) / 2 - cD),
         BC_E = abs((cB + cC) / 2 - cE),
         BC_F = abs((cB + cC) / 2 - cF),
         BC_G = abs((cB + cC) / 2 - cG),
         BC_H = abs((cB + cC) / 2 - cH),
         BC_FG = abs((cB + cC) - (cF + cG))
         ) %>%
  select(symbol, BC_FG)
```
